\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\addchap*{Acknowledgement}
\label{sec:acknowledgement}
%
First and foremost, I would like to thank my supervisor, Prof. Dr. Markus Axer.
Without his support and dedicated involvement every step of the way throughout the process, this thesis would never have come to fruition.
He has given me wonderful support throughout all these years.
I could always count on him no matter what the issues were.
\\
%
Furthermore, I would like to thank my reviewer, Prof. Dr. Gunnar Schr{\"o}der and Prof. Dr. Katrin Amunts.
I have always enjoyed our insightful discussions and am glad to have been guided through this work by you.
\\
%
I would also like to thank Prof. Katrin Amunts in her role as Institute Director of the INM-1 and Scientific Director of the Human Brain Project.
I am glad that you gave me the opportunity to participate in both the institute and the HBP.
\\
%
My special thanks go to my parents and my brother.
I would especially like to thank my father for giving me and my brother the curiosity for nature and thus for science.
My parents have always supported my brother in everything and we could always rely on them.
I would like to thank my brother for always helping me from a very young age, even though it was not always easy for him.
Without him, I probably would never have dared to tackle a science degree.
As a family, we have had to make very difficult decisions in recent years.
These decisions are anything but easy to make, but I am very grateful that we were able to make them together as a family and that we support each other.
\\
%
I would like to thank all my colleagues at INM-1 at the Forschungszentrum J{\"u}lich.
I felt very welcome from the beginning, and I still enjoy working with each and every one of you.
My particular thanks go to my dear colleague Miriam Menzel.
Without her scientific discussions, I would not have come as far as I have.
Unfortunately, she is leaving our working group, but she can continue to count on me, as I have always been able to count on her.
My further thanks go to Andrea Brandstetter.
She is a true friend and always there when I needed someone to talk to.
\\
%
Last but not least, I want to thank all of my friends.
I appreciate the various board game sessions and the hikes together.
Being with you guys is always a delight and a welcome diversion from my work when I need to unwind. 